Net title

### 2016-02-27 head.tex
give up simulation

\title{Cloud Manufacturing Ecosystem - Scheduling And Evolving}

\author[label1]{Author}
\address[label1]{ZJU}
\begin{abstract}
In the Cloud Manufacturing Ecosystem, a benign mode and scheduling methodology for massive services, which were contructed by resources is required, in order for the collaboration within the whole Industry Chain.
This paper 
\begin{inparaenum}[1)]
\item studied the features of the resources and services, then proposed a mode of Cloud Manufacturing;
\item modeled the services scheduling matter in the chain;
\item designed a simulation for the Cloud Manufacturing Ecosystem;
\item opened some Ecosystem related issues. 
\end{inparaenum}
With the use of Big-Data analysis on the Cloud Platform, resource optimization assessment/schedule methods could be developed, which could
gradually evolve the ecosystem to an optimal situation.

@@

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Cloud Manufacturing \sep Ecosystem \sep simulation \sep scheduling \sep optimization
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
\end{keyword}

>>>>

\title{Net title
%Cloud Manufacturing Ecosystem - Scheduling And Evolving
}

\author[label1]{Author}
\address[label1]{ZJU}
\begin{abstract}
New abstract
% In the Cloud Manufacturing Ecosystem, a benign mode and scheduling methodology for massive services, which were constructed standardly by resources is required, in order for the collaboration within the whole Industry Chain.
%This paper 
%\begin{inparaenum}[1)]
%\item studied the features of the resources and services, then proposed a mode of Cloud Manufacturing;
%\item modeled the services scheduling matter in the chain;
%\item designed evolving modules for the Cloud Manufacturing Ecosystem;
%\item opened some Ecosystem related issues. 
%\end{inparaenum}
%With the help of Data Science tools on the Cloud Platform, resource optimization assessment/schedule methods could be developed, which could
%gradually evolve the ecosystem to an optimal situation.

@@

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
new \sep key \sep words
%Cloud Manufacturing  Ecosystem \sep scheduling \sep evolving \sep optimization
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
\end{keyword}
